\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fancyvrb}
\title{WASP 2018 Foresight Report Comments}
\date{2018-11-21}
\author{Gustaf Waldemarson, Marcus Greiff, Pegah Nikbakht Bideh}

\usepackage{svg}

\usepackage{graphicx}
\usepackage{caption}

\usepackage{pgfplots}
\pgfplotsset{compat=1.8}
\usepackage{pgfplotstable}
\usepgfplotslibrary{groupplots}

\usetheme{wasp}

\graphicspath{{./graphics/}}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Collected Comments}

  \begin{itemize}
  \item Decide on a target audience for the document, reformulate it
    appropriately and choose an apt channel of communication for its
    distribution.

  \item More focus on security.

  \item Most topics related to Machine Learning and standards conclude that the
    current laws, standards and features of ML are incompatible. Then they
    conclude that the laws and/or standards should change, which feels like the
    wrong approach (for some applications at least).
    
  \end{itemize}
  
\end{frame}


\begin{frame}{General Comments}

  \begin{itemize}
  % \item Most topics in this reports are beyond my competence, but some things
  %   still stand out among the various topics.

  \item A lot of companies wants to be part of the research effort, but there
    seems to be a bit of a contention between sharing results within the company
    and with WASP as a whole - or even beyond WASP.

  % \item Perhaps WASP should put some effort into ensuring that some of the work
  %   done within WASP will actually benefit everyone? Possibly by ensuring that
  %   some work is Open Sourced?

  \end{itemize}

\end{frame}


\begin{frame}{General Comments}

  \begin{itemize}

  \item CPUs, GPUs and other accelerators are mostly treated as black boxes
    within WASP. Some more effort could probably be invested here for various
    topics - frameworks for software acceleration, special purpose accelerators,
    etc.

  \item One topic that appears to be missing is UX-research. This may become
    increasingly important, given that more and more tasks should supposedly be
    off-loaded to machines in the future.

    % \item Do not. ever. use. \url{booking.com} as a reference for anything good.
  \end{itemize}

\end{frame}


\begin{frame}{General Comments}

  \begin{itemize}
  \item The paper exclusively mentions the benefits of automation. To make the
    case for automation more potent, then it would be a good idea to bring up
    and address topics of the opposition.

  \item Good depiction of the laws that regulate and constrain the usage of
    UAVs, contrasted against the driving innovative forces in the industry, but
    should mention U-space initiative.

  \end{itemize}

\end{frame}


\begin{frame}{Public safety and security}
  \begin{itemize}
  \item In the challenges part, perhaps it is possible to present some Cyber
    threats or attacks, such as
    \begin{itemize}
    \item Dos
    \item Information leakage
    \end{itemize}
  \end{itemize}
\end{frame}


\begin{frame}{Smart Cities}
  \begin{itemize}
  \item There should be an added part to describe new technologies and trends in
    smart cities such as SDN (software defined networking)
  \item The benefits and advantages in comparison to traditional solutions
  \end{itemize}
\end{frame}


\bgroup
\setbeamertemplate{background}{}
\setbeamercolor{background canvas}{bg=black}
% \setbeamertemplate{navigation symbols}{}
\begin{frame}[t,plain]{}{}
  \begin{center}
    {\tiny \textcolor{white}{The End}}
  \end{center}
\end{frame}
\egroup

\end{document}
